---
title: "Project_ds"
author: "YI JUNG CHEN, CHUANMIN CHEN"
date: "2019/5/3"
output: word_document
---

#Yijung Chen did the first part and to the description. Chuanmin Chen did the rest part of text mining, regression tree and conclusion. Both of us did the shiny app together.

#resourse:https://www.kaggle.com/datasnaek/youtube-new
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Background

##The use of social media becomes popular nowadays. Specifically, Youtube is the world-famous video sharing website, and thousands of videos are uploaded and shared by Youtubers every day. In order to get more views and likes as possible, Youtubers not only need to improve the quality of videos they publish, but also need to satisfy what kinds of videos most viewers prefer.

#Question

###Video preferences differ from viewers. Besides, for objective factors, different publish time and time period can result in views of videos. For subjective factors, emotional changings can also lead to changes of video preferences and thus influencing views of videos. 

#Analytic Goal

###To help Youtubers effectively and efficaciously get more likes and views of their published videos, First of all, we will calculate what types of videos get the most views,likes, dislikes and comments respectively in order to getting insight into viewers' preferences. And next, we will analyze how is the effect of publish time on the views and likes of different types of videos and summarise what is the optimal publish time for videos to be published that can get the most attention. Furthermore, we did text analysis on video tags for the sake of helping Youtubers how to tag with words that can catch viewers' attention and satisfy their emotions.


```{r}
library(lubridate)
library(tidyverse)
library(ggplot2)
library(tidytext)
library(janeaustenr)
library(stringr)
library(gutenbergr)
library(modelr)
library(gapminder)
library(readxl)
library(gganimate)
library(scales)
library(shiny)
library(FNN)
library(cluster)
library(wordcloud)
library(reshape2)
```

#Dataset

#We collect the dataset from the link https://www.kaggle.com/datasnaek/youtube-new which is Trending YouTube Video Statistics. This YouTube dataset includes 10 different countries such as USA, Canda, and Great Britain.

#First, we select the USA data and the raw data has 16 columns. The raw data includes 16 variables, and 40950 samples. We cleaned part of our data in excel. We cut the column of trending_date to three column Year, month, and date. We also cut the column of publish_time and only keep the time its video published. Therefore, we got the new data including 18 variables. 

#We choose to analyse May,2018. It has 6199 samples with 15 variables after we selecting. From the next description part, we select category_id, views, likes, dislikes, and comment_count to create a new dataset called class_US.
```{r}
#clean dataset, choose May,2018 data
US = read.csv('USvideos.csv', header = T)
attach(US)
Year= ifelse(year=='17',2017,2018)
new_US = US%>%
  mutate(year = Year) %>%
   filter(year=='2018') %>%
  filter(month=='5')%>%
  mutate(date = make_date(year, month,day) )%>%
  select(-c(year,day,month,thumbnail_link))
new_US = na.omit(new_US)

class_US = new_US %>%
  group_by(category_id) %>%
  summarise(
    Views = sum(as.numeric(views)),
    lIKES = sum(as.numeric(likes)),
    Dislikes = sum(as.numeric(dislikes)),
    Comment = sum(as.numeric(comment_count))
  )


```

#Description

#First, we made four histograms to analyse which category_id has more views, likes, dislikes, and comments. There are 32 different kinds of categories. We found out that the category 10 Music vedio has the highest numbers of views, likes, dislikes, and comments. Also, the category 24 Entertainment video has the second highest numbers of views, likes, dislikes, and comments.
```{r}
#Which category has more views
class_US %>%
  ggplot(aes(category_id, Views))  + geom_bar(stat="identity") 

#Which category has more likes
class_US %>%
  ggplot(aes(category_id, lIKES)) + geom_bar(stat="identity") 

#Which category has more dislikes
class_US %>%
  ggplot(aes(category_id, Dislikes)) + geom_bar(stat="identity") 

#Which category has more comments
class_US %>%
  ggplot(aes(category_id, Comment)) + geom_bar(stat="identity") 

#10 is Music video category, 24 is Entertainment video category
```

#We extract category 10 (Music category) and 24 (Entertainment category) separately to see the top 5 channels. From the result of top 5 channels, the channel of ChildishGambino and ibighit have more views and likes. In addition, we did the top 5 channels in category 24. The channel of Sony Pictures Entertainment has more views and likes. Therefore, we think it is good for youtubers to publish videos about music or including some funny elements videos.
```{r}
#the top 5 channel title views in category 10
US%>%
  filter(category_id==10)%>%
  group_by(channel_title) %>%
  summarise(Views = sum(as.numeric(views))) %>%
  top_n(5)%>%
  ggplot(aes(channel_title, Views)) + geom_bar(stat="identity")

#the top 5 channel title likes in category 10 
US%>%
  filter(category_id==10)%>%
  group_by(channel_title) %>%
  summarise(lIKES = sum(as.numeric(likes))) %>%
  top_n(5)%>%
  ggplot(aes(channel_title, lIKES)) + geom_bar(stat="identity")

#the top 5 channel title dislikes in category 10
US%>%
  filter(category_id==10)%>%
  group_by(channel_title) %>%
  summarise(Dislikes = sum(as.numeric(dislikes))) %>%
  top_n(5)%>%
  ggplot(aes(channel_title, Dislikes)) + geom_bar(stat="identity")

#the top 5 channel title comments in category 10
US%>%
  filter(category_id==10)%>%
  group_by(channel_title) %>%
  summarise(Comment = sum(as.numeric(comment_count))) %>%
  top_n(5)%>%
  ggplot(aes(channel_title, Comment)) + geom_bar(stat="identity")

#the top 5 channel title views in category 24 (Entertainment)
US%>%
  filter(category_id==24)%>%
  group_by(channel_title) %>%
  summarise(Views = sum(as.numeric(views))) %>%
  top_n(5)%>%
  ggplot(aes(channel_title, Views)) + geom_bar(stat="identity")


#the top 5 channel title likes in category 24 
US%>%
  filter(category_id==24)%>%
  group_by(channel_title) %>%
  summarise(lIKES = sum(as.numeric(likes))) %>%
  top_n(5)%>%
  ggplot(aes(channel_title, lIKES)) + geom_bar(stat="identity")

#the top 5 channel title dislikes in category 24 
US%>%
  filter(category_id==24)%>%
  group_by(channel_title) %>%
  summarise(Dislikes = sum(as.numeric(dislikes))) %>%
  top_n(5)%>%
  ggplot(aes(channel_title, Dislikes)) + geom_bar(stat="identity")


#the top 5 channel title comments in category 24
US%>%
  filter(category_id==24)%>%
  group_by(channel_title) %>%
  summarise(Comment = sum(as.numeric(comment_count))) %>%
  top_n(5)%>%
  ggplot(aes(channel_title, Comment)) + geom_bar(stat="identity")

```

#Then, we transformed publish_time and only extract the hour of each video. Analysing the May, 2018 dataset about what time to publish videos would provide more likes and views by viewers. We found out the channels published from 10 a.m. to 3 p.m. would attract more people to like and provide more likes and views which is a good advise for youtubers to publish videos. Then, we did a graph about all channels which is published at 15. We can see that the channel of ibighit is also publish at 3 p.m.. Then, we did the top 10 of channel title which have more likes and views. The result shows that ibighit has the highest views and likes and ArianaGrandeVevo has the second highest number of views and likes. The rest of channels are almost from the category music and the category of entertainment.
```{r}
#When to publish videos will have more views and likes
Hour = hour(hms(new_US$publish_time))
US1 = new_US %>%
  mutate(timeline = Hour)

US1%>%
  group_by(timeline)%>%
  summarise(views=sum(views), likes=sum(likes))%>%
  ggplot(aes(timeline,views))+geom_point(aes(size=likes, fill=views), shape=21) + theme_bw() + labs(title="The best time publish videos") #publish at 15 has more likes and views

#the channel published at 15 
US1%>%
  filter(timeline==15)%>%
  group_by(channel_title)%>%
  mutate(like=sum(likes), view=sum(views))%>%
  select(timeline, channel_title, like, view)%>%
  ggplot(aes(x=like, y=view)) + geom_point()+geom_text(aes(label=channel_title))

#show the top 10 of channel title which have more likes and views
US1%>%
  filter(timeline==15)%>%
  group_by(channel_title)%>%
  summarise(likes=sum(likes), views=sum(views))%>%
  top_n(10)%>%
  ggplot(aes(x=likes, y=views)) + geom_point()+geom_text(aes(label=channel_title))

```


#Text mining

##To determine whether the videos will be viewed or not, video tags play an important role on attracting attention of viewers. Therefore, for the following step, we are going to analyse the most frequenct words displayed in video tags. Furthermore, we used sentiment analysis on the video tags trying to figure out what types of emotional intent of words do Youtubers use.

```{r}
text <-gsub('[^\u4e00-\u9fa5a-zA-Z0-9]'," ", US$tags)
text_df = data_frame(line = 1:length(text),
                     text = text)
head(text_df)
text_df = text_df %>%
  unnest_tokens(word,text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>% 
  anti_join(stop_words)
text_df = na.omit(text_df)
text_df %>%
  count(word, sort =T) %>%
  mutate(word = reorder(word,n)) %>%
  top_n(20) %>%
  ggplot(aes(word, n)) + 
  geom_col(aes(col = word)) + 
  xlab(NULL) + 
  coord_flip()

text1 <-gsub('[^\u4e00-\u9fa5a-zA-Z0-9]'," ", US1$tags)
text_df1 = data_frame(line = 1:length(text1),
                     text = text1)
text_df1 = text_df1 %>%
  unnest_tokens(word,text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>% 
  anti_join(stop_words)
text_df1 = na.omit(text_df1)
text_df1 %>%
  count(word, sort =T) %>%
  mutate(word = reorder(word,n)) %>%
  top_n(20) %>%
  ggplot(aes(word, n)) + 
  geom_col(aes(col = word)) + 
  xlab(NULL) + 
  coord_flip()
```

##By calculating the top 10 of most frequent words,the result shows that most people like watching videos related to make up. People also enjoy sorts of funny videos and music videos. However, we want to know if make sure make-up videos, music and funny videos are rendy recently. we then calculated the top 10 of most frequent words based on the data from Dec 2017 and found that the frequency of comedy and music were on the top5 while the frequency of make-up was at the least of top10. 


##Sentiment analysis
##In order to capturing emotional tone behind the words and understanding viewers' attitude, we did sentiment analysis on words and tried to find out feelings most people in this month.

```{r}
# select only the words from the nrc lexicon that are "positive"  and 'negative'words 
nrcnegative <- get_sentiments("nrc") %>% 
  filter(sentiment == "negative")

nrcpositive <- get_sentiments("nrc") %>% 
  filter(sentiment == "positive")

#Analysis on negative sentiment
negative_chapter <- text_df %>% 
  inner_join(nrcnegative) %>% 
  count(word) 
 
#Analysis on positive sentiment
positive_chapter <- text_df %>% 
  inner_join(nrcpositive) %>% 
  count(word) 


sentiment1 <- text_df %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
library(ggplot2)

sentiment1 %>% 
  top_n(20) %>%
  ggplot(aes(word, sentiment)) +
  geom_col(show.legend = FALSE) 

bing_word_counts <- text_df %>%
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
```

##As results shows, positive sentiment words are slightly higher than negative sentiment words.


#word cloud
```{r}
text_df %>%
  count(word) %>%
with(wordcloud(word, n, max.words = 100))
```

```{r}
text_df %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("blue", "red"),
                   max.words = 100)
```



```{r}
#Regression tree
library(tree)
n = length(US$views)
z = sample(n, n/2)
t = tree(likes~category_id + views + dislikes + comment_count + comments_disabled + ratings_disabled + video_error_or_removed, data = US[z,])
predict.t = predict(t, US)
mean((US$views-predict.t)[-z]^2)
plot(t, type = 'uniform');text(t)

```
###By using cross-validation method, we calculated the prediction MSE is 4.889367*10^13


###In conclusion, we find that in May 2018 music videos got the most views and likes, entertainment videos were the second most to be viewed and be liked, and more importantly, videos published during 10am-3pm would get more attentions. Compared to data from half past year, views of music videos and entertainment videos were both on the top 10 of the most views based on the text analysis. We can suggest that Youtubers can publish high-quality videos related to music and entertainment during 10am-3pm. Moreover, Youtubers can publish some related movie clips around the publish time of some special movies or around festivals. What is more, in May 2018 the most frequent word is make-up while in half past year it was the least of the top 10 frequency words. Therefore, we can know that make-up videos are trendy in this several months and give our suggestion that Youtubers can publish make-up videos in order to getting more views. Besides, if we have the inforamtion of comments from viewers, Youtubers can do sentiment analysis and know what viewers think of their videos and viewers think about their competitors. Finally, we tried to use regression tree as our prediction model but the extreme high value of prediction MSE indicated that it is not expected to be used in practice. 


#shiny app: https://kellychen.shinyapps.io/Project/
